# Week 6 Short Answer Questions

## Madelyn Nelson

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

12.1:
I believe that R Studio suggested facet_by as a function, though originally I was thinking of the facet_wrap() from ggplot.

``` {r} 
library(BabyNames)
```

```{r} 
BabyNames %>%
  facet_by(name) %>%
filter(rank(desc(total))<=5)  
```

12.2:

```{r}
Year_Above <- BabyNames %>%
  group_by(year) %>%
filter(rank(desc(total))<= 100) %>%
```
```{r}
Year_Below<-
  BabyNames%>%
  group_by(year) %>%
  filter(rank(asce(total))x<100)
```

```{r}
BabyNames %>%
group_by(year)
gather(key=filter(TRUE<-x %in% Year_Above, FALSE <-x %in% Year_Below), frac__in_top_100)
```


12.3:

a) summary
b) summary
c) transformation
d) transformation
e) neither
f) transformation
g) neither
h) transformation

SECTION 13

13.1:
  1) 8 Vertices
  2) 9 Edges

13.2:
  1) A, B, C, D are the vertices
  2) Table 3 shows the edges correctly
  3) Table 1 indicates that B connects to C, which it does not. Table 2 indicates that A connects to C but does not indicate that C subsequently connects to D
  
  13.3:
  
Table 2 gives the needed information to draw the graph.

13.4
  1) exports is mapped to the size of the letter
  2) population is mapped to the shape of the grey symbol
  
  SECTION 14:
  
  14.1:
  
  14.3: The most likely height for men is around 1.7. The most likely height for women is around 1.6. 

